Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-06-15 reports/manuscript.Rmd
Move sections around to match required format
Update affiliations

author: 
  - name          : "Taren Sanders*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "33 Berry St, North Sydney, NSW, Australia"
    email         : "Taren.Sanders@acu.edu.au"
  - name          : "Michael Noetel"
    affiliation   : "2"
  - name          : "Philip Parker"
    affiliation   : "1"
  - name          : "Borja Del Pozo Cruz"
    affiliation   : "3"
  - name          : "Stuart Biddle"
    affiliation   : "4, 13"
  - name          : "Rimante Ronto"
    affiliation   : "5"
  - name          : "Ryan Hulteen"
    affiliation   : "6"
  - name          : "Rhiannon Parker"
    affiliation   : "7"
  - name          : "George Thomas"
    affiliation   : "8"
  - name          : "Katrien De Cocker"
    affiliation   : "9"
  - name          : "Jo Salmon"
    affiliation   : "10"
  - name          : "Kylie Hesketh"
    affiliation   : "10"
  - name          : "Nicole Weeks"
    affiliation   : "1"
  - name          : "Hugh Arnott"
    affiliation   : "1"
  - name          : "Emma Devine"
    affiliation   : "11"
  - name          : "Roberta Vasconcellos"
    affiliation   : "1"
  - name          : "Rebecca Pagano"
    affiliation   : "12"
  - name          : "Jamie Sherson"
    affiliation   : "12"
  - name          : "James Conigrave"
    affiliation   : "1"
  - name          : "Chris Lonsdale"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia"
  - id            : "2"
    institution   : "School of Psychology, University of Queensland, Brisbane, Australia"
  - id            : "3"
    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark"
  - id            : "4"
    institution   : "Centre for Health Research, University of Southern Queensland, Springfield, Australia"
  - id            : "5"
    institution   : "Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia"
  - id            : "6"
    institution   : "School of Kinesiology, Louisiana State University, Baton Rouge, USA"
  - id            : "7"
    institution   : "The Centre for Social Impact, University of New South Wales, Sydney, Australia"
  - id            : "8"
    institution   : "The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia"
  - id            : "9"
    institution   : "Department of Movement and Sport Science, Ghent University, Ghent, Belgium"
  - id            : "10"
    institution   : "Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia"
  - id            : "11"
    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia"
  - id            : "12"
    institution   : "School of Education, Australian Catholic University, North Sydney, Australia"
  - id            : "13"
    institution   : "Faculty of Sport & Health Sciences, University of Jyväskylä, Finland"

>>>>

author: 
  - name          : "Taren Sanders*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "33 Berry St, North Sydney, NSW, Australia"
    email         : "Taren.Sanders@acu.edu.au"
  - name          : "Michael Noetel"
    affiliation   : "2"
  - name          : "Philip Parker"
    affiliation   : "1"
  - name          : "Borja Del Pozo Cruz"
    affiliation   : "3, 14, 15"
  - name          : "Stuart Biddle"
    affiliation   : "4, 13"
  - name          : "Rimante Ronto"
    affiliation   : "5"
  - name          : "Ryan Hulteen"
    affiliation   : "6"
  - name          : "Rhiannon Parker"
    affiliation   : "7"
  - name          : "George Thomas"
    affiliation   : "8"
  - name          : "Katrien De Cocker"
    affiliation   : "9"
  - name          : "Jo Salmon"
    affiliation   : "10"
  - name          : "Kylie Hesketh"
    affiliation   : "10"
  - name          : "Nicole Weeks"
    affiliation   : "1"
  - name          : "Hugh Arnott"
    affiliation   : "1"
  - name          : "Emma Devine"
    affiliation   : "11"
  - name          : "Roberta Vasconcellos"
    affiliation   : "1"
  - name          : "Rebecca Pagano"
    affiliation   : "12"
  - name          : "Jamie Sherson"
    affiliation   : "12"
  - name          : "James Conigrave"
    affiliation   : "1"
  - name          : "Chris Lonsdale"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia"
  - id            : "2"
    institution   : "School of Psychology, University of Queensland, Brisbane, Australia"
  - id            : "3"
    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark"
  - id            : "4"
    institution   : "Centre for Health Research, University of Southern Queensland, Springfield, Australia"
  - id            : "5"
    institution   : "Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia"
  - id            : "6"
    institution   : "School of Kinesiology, Louisiana State University, Baton Rouge, USA"
  - id            : "7"
    institution   : "The Centre for Social Impact, University of New South Wales, Sydney, Australia"
  - id            : "8"
    institution   : "The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia"
  - id            : "9"
    institution   : "Department of Movement and Sport Science, Ghent University, Ghent, Belgium"
  - id            : "10"
    institution   : "Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia"
  - id            : "11"
    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia"
  - id            : "12"
    institution   : "School of Education, Australian Catholic University, North Sydney, Australia"
  - id            : "13"
    institution   : "Faculty of Sport & Health Sciences, University of Jyväskylä, Finland"
  - id            : "14"
    institution   : "Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain"
  - id            : "15"
    institution   : "Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain"
